Supplementary material for: non-coding RNAs of bird genomes

### 2014-05-28 paper/supplementary-material.tex
Added common names to NCBI ID table.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|r|c|}
    \hline
RNA family (Rfam ID) & Chromosome & Coordinates & Strand \\
    \hline
\multicolumn{4}{|l|}{Macro-chromosomes:}\\
RNase MRP (RF00030)     & chr4 & 39276202-39276488 & -\\
\multicolumn{4}{|l|}{Micro-chromosomes:}\\ 
U4atac snRNA (RF00618)  & chr7 &	25702714-25702831 & +\\
RNase P RNA (RF00009)   & chr8 & 6609347-6609668   & -\\
Telomerase RNA (RF00024)& chr9 & 19429028-19429084 & +\\
Vault RNA (RF00006)     & chr13& 380747-380840     & +\\
U11 snRNA (RF00548)     & chr23& 2216932-2217058   & -\\
\hline
    \end{tabular}
  \end{center}
  \caption{The location of ``missing'' RNA families in the chicken genome (galGal4). }
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|l|l|}
    \hline
Species & BioProject ID & SRA ID & Study ID \\
    \hline
\emph{Chaetura pelagica} & PRJNA210808  & SRA092327 & SRP026688\\
\emph{Calypte anna} & PRJNA212866 & SRA096094 & SRP028275\\
\emph{Charadrius vociferus} & PRJNA212867 & SRA096158 & SRP028286\\
\emph{Corvus brachyrhynchos} & PRJNA212869 & SRA096200 & SRP028317\\
\emph{Cuculus canorus} & PRJNA212870 & SRA096365 & SRP028349\\
\emph{Manacus vitellinus} & PRJNA212872 & SRA096507 & SRP028393\\
\emph{Ophisthocomus hoazin} & PRJNA212873 & SRA096539 & SRP028409\\
\emph{Picoides pubescens} & PRJNA212874 & SRA097131 & SRP028625\\
\emph{Struthio camelus} & PRJNA212875 & SRA097407 & SRP028745\\
\emph{Tinamus guttatus} & PRJNA212876 & SRA097796 & SRP028753\\
\emph{Acanthisitta chloris} & PRJNA212877 & SRA097960 & SRP028832\\
\emph{Apaloderma vittatum} & PRJNA212878 & SRA097967 & SRP028834\\
\emph{Balearica regulorum} & PRJNA212879 & SRA097970 & SRP028839\\
\emph{Buceros rhinoceros} & PRJNA212887 & SRA097991 & SRP028845\\
\emph{Antrostomus carolinensis} & PRJNA212888 & SRA098079 & SRP028883\\
\emph{Cariama cristata} & PRJNA212889 & SRA098089 & SRP028884\\
\emph{Cathartes aura} & PRJNA212890 & SRA098145 & SRP028913\\
\emph{Chlamydotis macqueenii} & PRJNA212891 & SRA098203 & SRP028950\\
\emph{Colius striatus} & PRJNA212892 & SRA098342 & SRP028965\\
\emph{Eurypyga helias} & PRJNA212893 & SRA098749 & SRP029147\\
\emph{Fulmarus glacialis} & PRJNA212894 & SRA098806 & SRP029180\\
\emph{Gavia stellata} & PRJNA212895 & SRA098829 & SRP029187\\
\emph{Haliaeetus albicilla} & PRJNA212896 & SRA098868 & SRP029203\\
\emph{Haliaeetus leucocephalus} & PRJNA237821 & SRX475899 & SRP038924\\
                         & SRX475900   &           &          \\
                         & SRX475901   &           &          \\
                         & SRX475902   &           &          \\
\emph{Leptosomus discolor} & PRJNA212897 & SRA098894 & SRP029206\\
\emph{Merops nubicus} & PRJNA212898 & SRA099305 & SRP029278\\
\emph{Mesitornis unicolor} & PRJNA212899 & SRA099409 & SRP029309\\
\emph{Nestor notabilis} & PRJNA212900 & SRA099410 & SRP029311\\
\emph{Pelecanus crispus} & PRJNA212901 & SRA099411 & SRP029331\\
\emph{Phaethon lepturus} & PRJNA212902 & SRA099412 & SRP029342\\
\emph{Phalacrocorax carbo} & PRJNA212903 & SRA099413 & SRP029344\\
\emph{Phoenicopterus ruber} & PRJNA212904 & SRA099414 & SRP029345\\
\emph{Podiceps cristatus} & PRJNA212905 & SRA099415 & SRP029346\\
\emph{Pterocles gutturalis} & PRJNA212906 & SRA099416 & SRP029347\\
\emph{Tauraco erythrolophus} & PRJNA212908 & SRA099418 & SRP029348\\
\emph{Tyto alba} & PRJNA212909 & SRA099419 & SRP029349\\
\emph{Nipponia nippon} & PRJNA232572 & SRA122361 & SRP035852\\
\emph{Egretta garzetta} & PRJNA232959 & SRA123137 & SRP035853\\
\hline
    \end{tabular}
  \end{center}
  \caption{The NCBI BioProject/SRA and Study IDs used in this study. }
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|l|l|}
    \hline
Species & BioProject ID & SRA ID & Study ID \\
    \hline
\multicolumn{4}{|l|}{Genomes released before}\\
\hline
\emph{Aptenodytes forsteri} & PRJNA235982 & SRA129317 & SRP035855\\
\emph{Pygoscelis adeliae} & PRJNA235983 & SRA129318 & SRP035856\\
\emph{Gallus gallus} & PRJNA13342 & SRA030184 & SRP005856 (galGal4)\\
\emph{Taeniopygia guttata} & PRJNA17289 & SRA010067 & SRP001389\\
\emph{Meleagris gallopavo} & PRJNA42129 & Unknown & Unknown\\
\emph{Melopsittacus undulatus} & PRJEB1588 & ERA200248 & ERP002324\\
\emph{Anas platyrhynchos} & PRJNA46621 & SRA010308 & SRP001571\\
\emph{Columba livia} & PRJNA167554 & SRA054954 & SRP013894\\
\emph{Falco peregrinus} & PRJNA159791 & SRA055082 & SRP013939\\
\emph{Geospiza fortis} & PRJNA156703 & SRA051234 & SRP011940\\
\hline
\multicolumn{4}{|l|}{Outgroups}\\
\hline
\emph{Homo sapiens} & & & HG19/GRCh37\\
\emph{Alligator mississippiensis} & & & allMis1\\
\emph{Chelonia mydas} & PRJNA104937 & & \\
\hline
\multicolumn{4}{|l|}{RNA-seq data}\\
\hline
\emph{Gallus gallus} & PRJNA204941 & NA & NA \\
\emph{Gallus gallus} & NA & NA & SRP041863 \\
\hline
    \end{tabular}
  \end{center}
  \caption{The NCBI BioProject/SRA and Study IDs for the previously
    published genomes used in this study.}
\end{table}

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|r|c|}
    \hline
RNA family (Rfam ID) & Chromosome & Coordinates & Strand \\
    \hline
\multicolumn{4}{|l|}{{\bf Macro-chromosomes:}}\\
RNase MRP (RF00030)     & chr4 & 39276202-39276488 & -\\
\multicolumn{4}{|l|}{{\bf Micro-chromosomes:}}\\ 
U4atac snRNA (RF00618)  & chr7 &	25702714-25702831 & +\\
RNase P RNA (RF00009)   & chr8 & 6609347-6609668   & -\\
Telomerase RNA (RF00024)& chr9 & 19429028-19429084 & +\\
Vault RNA (RF00006)     & chr13& 380747-380840     & +\\
U11 snRNA (RF00548)     & chr23& 2216932-2217058   & -\\
\hline
    \end{tabular}
  \end{center}
  \caption{The location of ``missing'' RNA families in the chicken genome (galGal4). }
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|l|l|l|}
    \hline
Name & Species & BioProject ID & SRA ID & Study ID \\
    \hline
Chimney Swift & \emph{Chaetura pelagica} & PRJNA210808  & SRA092327 & SRP026688\\
Hummingbird & \emph{Calypte anna} & PRJNA212866 & SRA096094 & SRP028275\\
Plover & \emph{Charadrius vociferus} & PRJNA212867 & SRA096158 & SRP028286\\
Crow & \emph{Corvus brachyrhynchos} & PRJNA212869 & SRA096200 & SRP028317\\
Cuckoo & \emph{Cuculus canorus} & PRJNA212870 & SRA096365 & SRP028349\\
Manakin & \emph{Manacus vitellinus} & PRJNA212872 & SRA096507 & SRP028393\\
Hoatzin & \emph{Ophisthocomus hoazin} & PRJNA212873 & SRA096539 & SRP028409\\
Woodpecker & \emph{Picoides pubescens} & PRJNA212874 & SRA097131 & SRP028625\\
Ostrich & \emph{Struthio camelus} & PRJNA212875 & SRA097407 & SRP028745\\
Tinamou & \emph{Tinamus guttatus} & PRJNA212876 & SRA097796 & SRP028753\\
Rifleman & \emph{Acanthisitta chloris} & PRJNA212877 & SRA097960 & SRP028832\\
Trogon & \emph{Apaloderma vittatum} & PRJNA212878 & SRA097967 & SRP028834\\
Crane & \emph{Balearica regulorum} & PRJNA212879 & SRA097970 & SRP028839\\
Rhinoceros Hornbill & \emph{Buceros rhinoceros} & PRJNA212887 & SRA097991 & SRP028845\\
Nightjar & \emph{Antrostomus carolinensis} & PRJNA212888 & SRA098079 & SRP028883\\
Seriema & \emph{Cariama cristata} & PRJNA212889 & SRA098089 & SRP028884\\
Turkey Vulture & \emph{Cathartes aura} & PRJNA212890 & SRA098145 & SRP028913\\
Bustard & \emph{Chlamydotis macqueenii} & PRJNA212891 & SRA098203 & SRP028950\\
Mousebird & \emph{Colius striatus} & PRJNA212892 & SRA098342 & SRP028965\\
Sunbittern & \emph{Eurypyga helias} & PRJNA212893 & SRA098749 & SRP029147\\
Northern Fulmar & \emph{Fulmarus glacialis} & PRJNA212894 & SRA098806 & SRP029180\\
Red-throated Loon & \emph{Gavia stellata} & PRJNA212895 & SRA098829 & SRP029187\\
White-tailed Eagle & \emph{Haliaeetus albicilla} & PRJNA212896 & SRA098868 & SRP029203\\
Bald Eagle & \emph{Haliaeetus leucocephalus} & PRJNA237821 & SRX475899 & SRP038924\\
           &              & SRX475900   &           &          \\
           &              & SRX475901   &           &          \\
           &              & SRX475902   &           &          \\
Cuckoo Roller & \emph{Leptosomus discolor} & PRJNA212897 & SRA098894 & SRP029206\\
Bee-eater & \emph{Merops nubicus} & PRJNA212898 & SRA099305 & SRP029278\\
Brown Mesite & \emph{Mesitornis unicolor} & PRJNA212899 & SRA099409 & SRP029309\\
Kea & \emph{Nestor notabilis} & PRJNA212900 & SRA099410 & SRP029311\\
Pelican & \emph{Pelecanus crispus} & PRJNA212901 & SRA099411 & SRP029331\\
Tropicbird & \emph{Phaethon lepturus} & PRJNA212902 & SRA099412 & SRP029342\\
Cormorant & \emph{Phalacrocorax carbo} & PRJNA212903 & SRA099413 & SRP029344\\
Flamingo & \emph{Phoenicopterus ruber} & PRJNA212904 & SRA099414 & SRP029345\\
Grebe & \emph{Podiceps cristatus} & PRJNA212905 & SRA099415 & SRP029346\\
Sandgrouse & \emph{Pterocles gutturalis} & PRJNA212906 & SRA099416 & SRP029347\\
Turaco & \emph{Tauraco erythrolophus} & PRJNA212908 & SRA099418 & SRP029348\\
Barn Owl & \emph{Tyto alba} & PRJNA212909 & SRA099419 & SRP029349\\
Crested Ibis & \emph{Nipponia nippon} & PRJNA232572 & SRA122361 & SRP035852\\
Little Egret & \emph{Egretta garzetta} & PRJNA232959 & SRA123137 & SRP035853\\
\hline
    \end{tabular}
  \end{center}
  \caption{The NCBI BioProject/SRA and Study IDs used in this study. }
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|l|l|l|l|}
    \hline
Species & BioProject ID & SRA ID & Study ID \\
    \hline
Emperor Penguin & \emph{Aptenodytes forsteri} & PRJNA235982 & SRA129317 & SRP035855\\
Adelie Penguin & \emph{Pygoscelis adeliae} & PRJNA235983 & SRA129318 & SRP035856\\
Chicken & \emph{Gallus gallus} & PRJNA13342 & SRA030184 & SRP005856 (galGal4)\\
Zebra Finch & \emph{Taeniopygia guttata} & PRJNA17289 & SRA010067 & SRP001389\\
Turkey & \emph{Meleagris gallopavo} & PRJNA42129 & Unknown & Unknown\\
Budgerigar & \emph{Melopsittacus undulatus} & PRJEB1588 & ERA200248 & ERP002324\\
Mallard & \emph{Anas platyrhynchos} & PRJNA46621 & SRA010308 & SRP001571\\
Rock Pigeon & \emph{Columba livia} & PRJNA167554 & SRA054954 & SRP013894\\
Peregrine Falcon & \emph{Falco peregrinus} & PRJNA159791 & SRA055082 & SRP013939\\
Medium Ground-finch & \emph{Geospiza fortis} & PRJNA156703 & SRA051234 & SRP011940\\
\hline
\multicolumn{5}{|l|}{Outgroups}\\
\hline
Human & \emph{Homo sapiens} & & & HG19/GRCh37\\
Alligator & \emph{Alligator mississippiensis} & & & allMis1\\
Green Turtle & \emph{Chelonia mydas} & PRJNA104937 & & \\
\hline
\multicolumn{5}{|l|}{RNA-seq data}\\
\hline
Chicken & \emph{Gallus gallus} & PRJNA204941 & NA & NA \\
Chicken & \emph{Gallus gallus} & NA & NA & SRP041863 \\
\hline
    \end{tabular}
  \end{center}
  \caption{The NCBI BioProject/SRA and Study IDs for the previously
    published genomes used in this study.}
\end{table}
